Report - September 2017

### 2017-09-20 report.Rmd
added code to plot the most recent data from the repo against the most recent forecast prior to that data collection.  there are still some issues, right now this will only work when June 2017 is the most recent data

>>>>

---
title: "Report - September 2017"
---
Here's the most recent data (blue) compared to the forecast performed right before data collection (black, with error bars)
```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("forecast_tools.R")

# get most recent rodent data
rodents = abundance("repo", shape='flat')
period_code = max(rodents$period)
observed = dplyr::filter(rodents, period == period_code)

# get new moon number associated with this period
newmoons_table = read.csv(text = getURL("https://raw.githubusercontent.com/weecology/PortalData/master/Rodents/moon_dates.csv"))
moon_code = dplyr::filter(newmoons_table,period==period_code) %>% select(newmoonnumber) %>% as.integer()

# get most recent forecast prior to data collection -- WIP!!!!!!!! there's an issue up
data = read.csv('predictions/2017-06-23Allforecasts.csv',na.strings = '')
data = plyr::rename(data,c('NewMoonNumber' = 'newmoonnumber'))

ensemble = dplyr::filter(data, level == 'All', model == 'Ensemble', newmoonnumber==moon_code)
sp_predictions = get_sp_predicts(ensemble, 'All', lead_time = 1)

joined_data = left_join(sp_predictions, observed, by = "species")
joined_data[is.na(joined_data)] = 0
joined_data[joined_data$species=='total','abundance'] = sum(joined_data$abundance,na.rm=T)
joined_data[joined_data$species=='total','period'] = period_code

sp_predict = plot_species_forecast(sp_predictions)  
sp_predict = sp_predict + geom_point(data = joined_data, mapping = aes(x = abundance, y = species),
             color = "blue")
plot(sp_predict)
```
